Data Preparation

### 2019-03-12 Data Preparation.Rmd
correct type of time var in d_transcript df
add TODO list

@@

    # Combine year and period to have be able to order the course in time using a single variable
    time = str_c(Year_numerical, period_numerical)

>>>>

TODO:

* when student takes a course multiple times:
    * keep lowest grade
    * keep highest grade 
    * or keep both (much more complex)

@@

    # Combine year and period to have be able to order the course in time using a single variable
    time = str_c(Year_numerical, period_numerical) %>% as.numeric,

    grade_ceil = ceiling(Grade)
